### 2016-08-22 ms/ms.tex
modified discussion

Using a long-term data-set of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., changing points). Even with changing points in
interaction organization, networks could still be assembling via
preferential attachment if the network reorganizations were primarily
driven the by peripheral, temporally variable species while a stable,
well-connected core of species still persists. We thus examine whether
the species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species.  Lastly, we examine whether networks are
assembling toward predictable interaction patterns, and the
ramifications for the robustness of the networks to species extinction
and perturbation.

@@

We also explored how the robustness to cascading effects changed as
community assembled, using algebraic connectivity--- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic}--- as a proxy for network robustness
(e.g. Gaiarsa et al., submitted). Algebraic connectivity was first
used to describe spectral properties of complex graphs other than
ecological networks, and it has been extensively studied \citep[e.g.,][]{fiedler1973algebraic, costa2007characterization, mohar1991laplacian, de2007old}.   Algebraic connectivity is related to the mean diameter of a graph and to how difficult it is to turn
a network into completely disconnected groups of nodes, or species
\citep{costa2007characterization}--- the larger the algebraic connectivity, the more robust a
network is to cascading effects (e.g. Gaiarsa et al., submitted), and the harder it is to break the community into isolated groups of species.

@@

In contrast, the robustness of networks to perturbation, as measured
by the algebraic connectivity of the network, increased as the network
assembled (estimate of the slope of robustness through time $\pm$
standard error of the estimate, $0.6814 \pm 0.272$, $p$-value=$0.042$,
Fig.~\ref{fig:rob}).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not possible, even though two changing points did occur in the non assembling hedgerow six between 2009 and 2010, and 2010 and 2011 (HR6, Fig.~\ref{fig:changePoints}). Interestingly, most of the assembling hedgerows did
not undergo a significant reorganization of interactions immediately
the hedgerow was planted (i.e., the transition from weedy field margin
to hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollintor communities (Kremen and
M'Gonigle, in prep).

Given that changing ponts did occur, we then turned to explore how these changing points came to be, and what species were responsible for it. Ecolgical theory predicts that species abundance is positively correlated to number of interaction partners a species has (degree \citep{Bluthgen2007}). Thus, we expected that the more abundant species would be more persisten through network assembly, and would contribute the least to the changing points. Surprisingly however, we encountered the opposite: the species that were most variable in
their network position and thus contributed most to network
reorganizations where species with the highest degrees (i.e., most
generalized) and persistence. For example, the five most ubiquitous
species in our study landscape --- \textit{Halictus ligatus},
\textit{Halictus tripartitus},\textit{Lasioglossum (Dialictus)
  incompletum}, and \textit{Toxomerus marginatus} --- were the
only species that changed what module (i.e., community), and they were also 
present in across years in all of the assembling hedgerows. Because
species degree and persistence were strongly correlated, it is
difficult to disentangle the causal mechanism for why species with
those characteristics are so variable in their network
position. Generalized species may be able to better exploit the limited
floral resources the intensively managed agriculture landscape, and
thus also most persistent. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a higher degree. Either way, our result suggests
that adaptable species can change their network position to utilize
the most advantageous floral resources available, which my depend the other
pollinator species that are present and the state of the floral
resource. Thus given the opportunity and ability to use different
resources, species will often change their network positions.

@@

The frequent changing points in network organization, dynamic nature
of the location of species in networks, and turnover of species and
nodes all point to an assembly mechanism other than preferential
attachment. Nestedness did increase with years post restoration, as
would be expected if colonizing, specialist species attached to a
central, pre existing generalist core \cite{albrecht2010plant}. With preferential
attachment, however, we would also expect connectance and
specialization to increase, and we found no such trends. The stable level
of network-level specialization through the assembly process may be
due to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness.

The changes in network patterns with assembly also increased the
robustness of the networks to perturbation -- providing further
evidence that hedgerows are valuable tool for promoting species
conservation and ecosystem provision in agricultural areas
\citep{mgonigle-2015-x, ponisio2015farm, kremen-2015-602}. Because the
vulnerability of the network to cascading effects, as
measured by algebraic connectivity, is correlated with species
richness, the increase and plant and pollinator richness following
restoration is at least partially responsible for enhancing network
robustness to cascading effects. This result contributes to the stability and diversity debate indicating that diversity might promote statibility, even though there are contrasting results in the literature \citep [e.g.][]{may1972will, pimm1984complexity, montoya2006ecological}. However, the robustness of ecological communities to disturbances  might depend on the identity of the species mostly being affected by the disturbance (REF). For example, networks might be more sensible to the disturbance of a generalist when compared to a specialist (REF).

>>>>

Using a long-term data-set of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., changing points). Even with changing points in
interaction organization, networks could still be assembling via
preferential attachment if the network reorganizations were primarily
driven the by peripheral, temporally variable species while a stable,
well-connected core of species still persists. We thus examine whether
the species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species.  Lastly, we examine whether networks are
assembling toward predictable interaction patterns, and the
ramifications for the robustness of the networks to species extinction
and cascading perturbations.

@@

We also explored how the robustness to cascading effects changed as
community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity is related to the
mean diameter of a graph and to how difficult it is to turn a network
into completely disconnected groups of nodes, or species
\citep{costa2007characterization} --- the larger the algebraic
connectivity, the more robust a network is to cascading effects
(Gaiarsa et al., submitted), and the harder it is to break the
community into isolated groups of species.

%% marilia:
%% I'm not totally sure what this adds to the methods. Since most
%% people reading this paper will not understand what "spectral
%% properties" are (I don't in fact =/ ) it is a bit of a misdirection
%% since we are not interested in it. I think it is enough to point to
%% your paper which is using the Alg Con the way we want to.

%% removed:
% Algebraic connectivity is
% used to describe spectral properties of complex graphs other than
% ecological networks \citep[e.g.,][]{fiedler1973algebraic,
%   costa2007characterization, mohar1991laplacian, de2007old}.

% what's the mean diameter of a graph? Also can we use the
%% term network instead of graph to be mote consistent with the rest
%% of the methods? We use graph a bit in the change point section, but
%% I think it is explained a bit better there?

%% I also removed the e.g.'s because your paper is all we want to
%% cite, and not "for example Gariarsa et al."

@@

In contrast, the robustness of networks to cascading perturbations, as
measured by the algebraic connectivity of the network, increased as
the network assembled (estimate of the slope of robustness through
time $\pm$ standard error of the estimate, $0.6814 \pm 0.272$,
$p$-value=$0.042$, Fig.~\ref{fig:rob}).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not possible. Interestingly, most of the assembling hedgerows did
not undergo a significant reorganization of interactions immediately
the hedgerow was planted (i.e., the transition from weedy field margin
to hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollintor communities (Kremen and
M'Gonigle, in prep).

Given that several changing points in network organization occured
during assembling, we next explored the species most likely
responsible for the observed shifts in interaciton patterns. Based on
a preferential attachment-like mechanism, we expect that the most
persistent and high degree species would remain stable in the network
core during assembly, and would thus contribute the least to the
changing points in network organization. Surprisingly however, we
encountered the opposite: the species that were most variable in their
network position and thus contributed most to network reorganizations
where species with the highest degrees (i.e., most generalized) and
persistence. For example, the five most ubiquitous species in our
study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
what module (i.e., community), and they were also present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources the intensively managed
agriculture landscape, and thus also most persistent. More persistent
species also have longer phenologies, so they have the opportunity to
visit many different flowers, resulting in a higher degree. Either
way, our result suggests that adaptable species can change their
network position to utilize the most advantageous floral resources
available, which my depend the other pollinator species that are
present and the state of the floral resource. Thus given the
opportunity and ability to use different resources, species will often
change their network positions.

@@

The frequent changing points in network organization, dynamic nature
of the location of species in networks, and turnover of species and
nodes all point to an assembly mechanism other than preferential
attachment. Nestedness did increase with years post restoration, as
would be expected if colonizing, specialist species attached to a
central, generalist core \cite{albrecht2010plant}. With preferential
attachment, however, we would also expect connectance and
specialization to increase, and we found no such trends. The stable
level of network-level specialization through the assembly process may
be due to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness.

The changes in network patterns with assembly also increased the
robustness of the networks to cascading perturbations -- providing
further evidence that hedgerows are valuable tool for promoting
species conservation and ecosystem provision in agricultural areas
\citep{mgonigle-2015-x, ponisio2015farm, kremen-2015-602}. Because the
vulnerability of the network to cascading effects, as measured by
algebraic connectivity, is correlated with species richness, the
increase and plant and pollinator richness following restoration is at
least partially responsible for enhancing network robustness to
cascading effects. The relationship between diversity and stability in
networks has been the subject of considerable debate
\citep[e.g.,][]{may1972will, pimm1984complexity,
  montoya2006ecological}. Our results provides one of the few
empirical examples of how restoring species diversity contributes to
enhancing network stability. Through these hedgerows were designed to
promote floral resrouces across the growing season and not
specifically to promote any specific network properties
\citep{menz-2010-4}, the pollinators assembled into resilent
interaction patterns. With prior knowledge of the floral preferences
of pollinators, future restoration efforts may also be able to
incorporate promoting network stability into planning efforts
\citep{mgonigle2016tool}

%% marilia: not totally sure where you are going here. I was thinking
%% it could be expanded into a whole paragraph on the fact that we
%% don't really understand what effects species persistence, and how
%% that is problematic with understanding netwokr robustness. But
%% maybe it is a bit too far removed from the main message of the
%% paper? Maybe something could be added in the last papergraph about
%% needed more mechanistic models?

%  However, the robustness of ecological
% communities to disturbances might depend on the identity of the
% species mostly being affected by the disturbance (REF). For example,
% networks might be more sensible to the disturbance of a generalist
% when compared to a specialist (REF).
